\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tikzsymbols}
\usepackage{float}

\lstset{
    basicstyle=\ttfamily,
    backgroundcolor=\color{gray!30},
}

\begin{document}
\title{Overview}

\graphicspath{ {./Images/} }
\tableofcontents

\section{Introduction}
The goal of these documents is to provide a baseline foundation for the Windows team members.
Please update and improve the documentation wherever you see fit.

I think there are 5 categories to cover:

\begin{enumerate}
        \item Deployment to Proxmox
        \item Setup of Active Directory
        \item Setup of the CA
        \item Setup of the DFS / highly available files
        \item Hardening
        \item Planning (for the competition, timelines)
        \item Offense (to practice)
        \item Powershell commands (to reference in one spot)
\end{enumerate}

Each category has an associated folder

This is my knowledge of Windows. I have tried to include everything I think could be useful to you.
I encourage you to do the same, add more sections and flesh out the sections with your own experience.

I made a dedicated powershell pdf so we can easily reference them.
Note that powershell commands are not case sensitive.

There could be unpatched CVEs during the competition. A list of them can be found \href{https://stack.watch/product/microsoft/windows-server-2019/}{here}.
For example, CVE-2020-0796 was severe and would surely have been used by the red team.

You will be using Remmina a lot, make sure to click "share folder" to send files over RDP.
The folder is visible under "This PC".
Windows defender can remove files from the share folder.
\end{document}