\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tikzsymbols}
\usepackage{float}
\usepackage{epigraph}
\usepackage{changepage}

\lstset{
    basicstyle=\ttfamily,
    backgroundcolor=\color{gray!30},
}

\renewcommand{\epigraphflush}{flushleft}

\title{Offense}
\begin{document}
\maketitle

\graphicspath{ {./Images/} }

\title{Windows Offense}

\tableofcontents

\section{Introduction}
\epigraph{If you know the enemy and know yourself, you need not fear the result of a hundred battles.}{Sun Tzu}

To be a good blue team, we should practice red teaming.

\section{Covenant Malware}
Covenant is a .NET command and control framework. It works by installing
Grunts on the target machine. Grunts work like reverse shells, they connect to a listener on 
the C2 server.

You should install covenant on whatever computer you
plan to use as the C2 server. This will let you control the windows machines. 
Covenant requires GIT and .NET to work. 
You will also need to install .NET on the victim machine.

\begin{itemize}
        \item\href{https://github.com/cobbr/Covenant/wiki/Installation-And-Startup}{Instructions on their GitHub}
        \item \href{https://blog.netwrix.com/2022/12/16/covenant-c2-tutorial/}{Blog Tutorial}
        \item \href{https://github.com/cobbr/Covenant-wiki/blob/master/Listeners.md}{More information on listeners}
\end{itemize}

To install GIT on windows, go here:
\href{https://git-scm.com/download/win}{https://git-scm.com/download/win}

To install .NET, you can download it from the
\href{https://dotnet.microsoft.com/en-us/download}{website} or you can install it in server manager (in the "Features" menu).

To install .NET on linux, follow these 
\href{https://learn.microsoft.com/en-us/dotnet/core/install/linux-scripted-manual#scripted-install}{directions}


After installing the dependencies, we can install and run covenant with:

\begin{lstlisting}
git clone --recurse-submodules https://github.com/cobbr/Covenant
cd Covenant/Covenant
dotnet build
dotnet run
\end{lstlisting}

"After running these commands, the Covenant service should be up and running. 
You can then browse to the Covenant application interface on its default web port of 
7443 to set up a user account and begin using the framework." -Bing

If you would like to have listeners on ports 1-1023, you should run Covenant as root.

The web console can be accessed at https://127.0.0.1:7443 and not localhost:7443, as the https is important

For the Grunt to work, .NET has to be installed on the victim.

Anti Grunt countermeasures:
"If you uninstall the .NET Framework 3.5 from the victim machine, 
it is likely that the Grunt will stop working." -Bing.
I think it is very funny that malware has dependencies.

\subsection{Troubleshooting the VPN}
I tried a lot of ways to get the Grunt to recognize my machine.
The only solutions that worked are a Kali VM or \href{sec:CloudflareTunnels}{Cloudflare Tunnels}.

To get your IP address from the RDP connection:
\begin{enumerate}
\item Open the Command Prompt by pressing the Windows key + R and typing cmd.
\item Type netstat -n | find ":3389" and press Enter. This will display a list of active connections to the RDP port (3389).
\item Look for the connection that corresponds to your RDP session. The IP address of the RDP client will be listed next to the ESTABLISHED entry.
\end{enumerate}

\href{https://youtu.be/Fi0jXm8VOFU}{Advanced Usage of Covenant}

\section{Cloudflare Tunnels}
\label{sec:CloudflareTunnels}

Justin mentioned how he was going to connect to the machines using cloudflare tunnels. So I will practice that and document it.

\begin{enumerate}
\item You can use your own domain, or you can have cloudflare provide one for you.
\item You need to install cloudflared on the machines you are connecting to
\item To install on proxmox:
\begin{adjustwidth}{-5cm}{}
\begin{lstlisting}
wget -q 
https://github.com/cloudflare/cloudflared/releases/latest/download/cloudflared-linux-amd64.deb 
&& sudo dpkg -i cloudflared-linux-amd64.deb
\end{lstlisting}
\end{adjustwidth}
    
\item To do it without a domain: cloudflared tunnel --url http://localhost:80

\item Take note of the random url generated.

\item cloudflared access tcp --hostname randomsubdomain.trycloudflare.com --url tcp://localhost:5900
\end{enumerate}
\section{BloodHound}
BloodHound is a tool that maps out Active Directory (AD) relationships and 
permissions, turning them into clear visual graphs. It helps both defenders
and attackers see potential security risks within AD environments, making 
it easier to spot vulnerabilities or misconfigurations.

\section{WinPeas}
Windows Privilege Escalation Scripts.

This script dumps a bunch of information about potentially interesting things to look for on
the windows machine. It can be found \href{https://github.com/carlospolop/PEASS-ng/tree/master/winPEAS}{here}.
 

\section{SMBGhost / EternalDarkness / CVE-2020-0796}
SMBGhost (CVE-2020-0796), also referenced as EternalDarkness, 
is a severe vulnerability in Microsoft's Server Message Block (SMB) 
3.1.1 protocol. This flaw permits unauthenticated remote attackers to 
execute arbitrary code on vulnerable systems.

This could be important to understand as it is a significant vulnerability in old Windows Server systems.
TODO: add more potential vulnerabilities, explain this one more.

\begin{itemize}
    \item \href{https://blog.zecops.com/research/exploiting-smbghost-cve-2020-0796-for-a-local-privilege-escalation-writeup-and-poc/}{ZecOps Blog on SMBGhost} - Writeup and PoC on exploiting SMBGhost (CVE-2020-0796) for local privilege escalation.
    \item \href{https://github.com/carbonblack/tau-tools/tree/master/remediation/EternalDarkness}{Carbon Black's EternalDarkness Remediation} - Detecting and remediating the EternalDarkness vulnerability.
    \item \href{https://blogs.vmware.com/security/2020/03/threat-analysis-cve-2020-0796-eternaldarkness-ghostsmb.html}{VMware's Threat Analysis on EternalDarkness} - VMware's analysis of EternalDarkness/GhostSMB.
    \item \href{https://www.cisa.gov/news-events/alerts/2020/06/05/unpatched-microsoft-systems-vulnerable-cve-2020-0796}{CISA Alert on CVE-2020-0796} - CISA giving resources on EternalDarkness/GhostSMB.    
\end{itemize}

\section{Malware to look into}
Here is some random stuff so I don't forget to look into it:
\begin{itemize}
    \item \href{https://github.com/0x44F/WinKit}{WinKit} - A collection of useful Windows utilities and configurations.
    \item \href{https://github.com/D4stiny/spectre}{Spectre} - Tool for generating payload delivery scripts.
    \item \href{https://github.com/DarkCoderSc?tab=repositories}{DarkCoderSc's repositories} - Contains various hacking and penetration testing tools, notably ones focused on Windows exploitation.
    \item \href{https://en.wikipedia.org/wiki/DarkComet}{DarkComet} (infected file, do not run on main OS: \href{https://github.com/zxo2004/DarkComet-RAT-5.3.1}{GitHub Link}) - A Remote Access Trojan (RAT) that allows control over infected devices.
    \item \href{https://github.com/quasar/Quasar}{Quasar} - An open-source RAT for Microsoft Windows operating systems.
    \item \href{https://github.com/screetsec/TheFatRat}{TheFatRat} - A tool for generating backdoor payloads and bypassing common anti-virus solutions.
    \item \href{https://github.com/DarkCoderSc/win-brute-logon}{win-brute-logon} - A tool for bruteforcing login credentials on Windows systems.
    \item \href{https://github.com/Hackplayers/evil-winrm}{evil-winrm} - 
\end{itemize}

\section{Real Administration Software to try}
\begin{itemize}
    \item \href{https://www.islonline.com/us/en/}{ISL Online} - Remote desktop and support software solution.
    \item \href{https://devolutions.net/remote-desktop-manager/}{Remote Desktop Manager by Devolutions} - Software for managing multiple remote connections efficiently.
\end{itemize}
    
\end{document}

